---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

# ShinyLEGO: Create LEGO mosaics directly from R and Shiny

__ShinyLEGO__ is a Shiny application that lets you create a simulated mosaic composed of LEGO bricks from any image file. Once your picture is uploaded, you can customize various settings for your mosaic such as dimensions, brightness, and color types.  In addition, the application will generate specific instructions so that you can build the mosaic yourself!  These instructions contain the brick colors and types required for each step, and a diagram showing how the bricks are to be assembled.  

This application would not be possible without the innovative R scripts created by [Ryan Timpe](http://www.ryantimpe.com/)!  Ryan has written excellent blogposts detailing the workflow this application draws upon, and the code for each post can be found on his [LEGOMosaics GitHub repository](https://github.com/ryantimpe/LEGOMosaics):

* [How To: LEGO mosaics from photos using R & the Tidyverse](http://www.ryantimpe.com/post/lego-mosaic1/)
* [LEGO mosaics: Two weeks later](http://www.ryantimpe.com/post/lego-mosaic2/)
* [LEGO mosaics: Part 3(D)](http://www.ryantimpe.com/post/lego-mosaic3/)

## Installation

You can install the development version of `shinylego` from [GitHub](https://gitlab.com) with:

``` r
# install.packages("remotes")
remotes::install_github("rpodcast/shinylego")
```

## Usage

Once you have installed the package, you can run the application within your R session using the following command:

```{r example, eval=FALSE}
shinylego::run_app()
```

## Deployments

`shinylego` is also available on the Shinyapps.io hosting service at [rpodcast.shinyapps.io/shinylego](https://rpodcast.shinyapps.io/shinylego)

## Acknowlegements

In addition to Ryan Timpe's excellent R programs detailed above, this application utilizes many powerful packages in the `shiny` ecosystem such as the following:

* [`shinyjs`](https://deanattali.com/shinyjs): Easily improve the user experience of your Shiny apps in seconds by [Dean Attali](https://deanattali.com/)
* [`bs4Dash`](https://rinterface.github.io/bs4Dash/index.html): Bootstrap 4 shinydashboard using AdminLTE3  by [David Granjob](https://twitter.com/divadnojnarg) (part of the [RinteRface](https://rinterface.com/) initiative)
* [`shinyWidgets`](https://dreamrs.github.io/shinyWidgets/index.html): Extend widgets available in Shiny by [Victor Perrier](https://twitter.com/_pvictorr) (part of the [dreamRs](https://www.dreamrs.fr/) organization) 
* [`shinycustomloader`](https://emitanaka.github.io/shinycustomloader/): Add a custom loader for R shiny by [Emi Tanaka](https://emitanaka.github.io/)
* [`DT`](https://rstudio.github.io/DT): R Interface to the jQuery Plug-in DataTables by [Yihui Xie](https://yihui.name/)
* [`golem`](https://github.com/ThinkR-open/golem/): A framework for building robust Shiny Apps by [Vincent Guyader](https://github.com/VincentGuyader) and [Colin Fay](http://colinfay.me/) (part of the [R Task Force](https://rtask.thinkr.fr/) at [ThinkR](https://thinkr.fr/))

## CoC

Please note that the 'shinylego' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

